Using traffic analysis to identify The Second Generation Onion Router

### 2011-02-26 thesis/thesis.tex
Confounding variables, not independent. Conclusion and implications of results.

The experiment conducted in this paper utilize a non-equivalent group design.
The experimental groups are generated using simulations which allow for a great
deal of control over independent variables, ensuring minimal difference between
the control and treatment groups. Both experiment groups perform the exact same
simulations. The control group performs all simulations using regular HTTPS,
while the treatment group proxies all communications over Tor. The treatment
group can be broken into HTTP over Tor and HTTPS over Tor based simulations.

@@

@@

While it is difficult to draw a broad conclusion with the limited nature of the
experiment conducted, the findings suggest that the strategies used by anonymous
networks to thwart identity revealing traffic analysis may make them easier to
identify.

Research has shown that the low latency design of Tor means it is vulnerable to
traffic analysis attacks that correlate traffic patterns with users. This
transparency should in fact make Tor more difficult to classify than more
'anonymous' network designs which employ batching and traffic normalizing.
Steganography is a difficult problem and it may be that the extra traffic
required to maintain the Tor network means it will always be easily
differentiated from regular encrypted traffic.

>>>>

The experiment conducted in this paper utilize a non-equivalent group design.
The experimental groups are generated using simulations which allow for a great
deal of control over confounding variables, ensuring minimal difference between
the control and treatment groups. Both experiment groups perform the exact same
simulations. The control group performs all simulations using regular HTTPS,
while the treatment group proxies all communications over Tor. The treatment
group can be broken into HTTP over Tor and HTTPS over Tor based simulations.

@@

The research results suggest that the strategies used by anonymous networks to
hide the identity of network participants, may make those anonymous networks
more easy to distinguish from networks and software that do not provide any
anonymity.

Research has shown that the low latency design of Tor means it is vulnerable to
traffic analysis attacks that correlate traffic patterns with users. This
vulnerability is indicative of the subtle amount of overhead incurred when
sending traffic through Tor. This should make it difficult to identify whether a
connection is using Tor VS not using Tor, though it is clearly still possible.
Reducing this overhead further may reduce the success of Tor traffic
identification.

Stronger anonymity providing networks utilize more sophisticated techniques to
hide individual identities such as batching, queuing and normalization. While
they may be more resistant to identity uncovering attacks, this may also make
them more easily identifiable by classification techniques.

@@

Using Tor as a communications proxy incurs some overhead, sufficient enough that
when using a Tor proxy in controlled conditions, Tor traffic can be
distinguished from regularly encrypted traffic. This overhead may be sufficient
enough that Tor nodes in a real world network can be identified by using readily
available eavesdropping techniques.

However, the experiment was based on a small set of simulated data, with which
it would be impossible to cover all the possible real world conditions. The
variability present in the real Tor network may make this classification
technique impossible. Further research needs to be conducted with live packet
traces from real participants in the Tor network.
